Structured Versus Decorated Cospans

### 2020-11-25 cospans.tex
fixed typo in references

\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, \textsl{Eilenberg, Samuel, et al., eds. Proceedings of the Conference on Categorical Algebra: La Jolla 1965},  Springer, Berlin, 1966, pp.\ 21--83.

>>>>

\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, in \textsl{Proceedings of the Conference on Categorical Algebra: La Jolla 1965}, eds.\ S.\ Eilenberg \textit{et al}, Springer, Berlin, 1966, pp.\ 21--83.
